\documentclass[12pt]{article}
\usepackage[dvips]{epsfig}
\usepackage{color}
\usepackage{url}
\usepackage[colorlinks=true]{hyperref}

\begin{document}

\section*{GENESIS: Documentation}

{\bf Related Documentation:}
% start: userdocs-tag-replace-items related-do-nothing
% end: userdocs-tag-replace-items related-do-nothing

\section*{Introduction to the GENESIS Shell}

After GENESIS has completed its startup procedure you should see the command prompt, {\tt genesis $>$}, indicating that you are now in the GENESIS shell environment ({\bf G-Shell}) and running an interactive GENESIS session. Note that to provide backward compatibility, the {\bf G-Shell} interfaces with the Script Language Interpreter (SLI) of previous versions of GENESIS. To learn more about that functionality see \href{../backward-compatibility/backward-compatibility.tex}{here}.
%It is possible to excute both UNIX and {\bf G-Shell} commands from within the {\bf G-Shell}. However, UNIX shell commands must use an appropriate Perl system call, e.g. ``{\tt system(`echo ``Hello, World''')}'' will return ``{\tt Hello,\,World!}''.

One feature of the {\bf G-Shell} is that it is important to have only one model loaded during a GENESIS session. Currently, there are two ways to change a model:

\begin{enumerate}

\item Exit the {\bf G-Shell}, start a new GENESIS session, then load the new model  via the {\tt ndf\_load} command. Importantly, don't forget that to save changes made to a model between GENESIS sessions, you must save the model prior to deleting it (via the {\tt ndf\_save} command--see \href{../tutorial1/tutorial1.tex}{Save Model} for details).

\item Alternatively, a faster and more convenient way to replace a model within a GENESIS session is to use the {\tt delete\_current\_model} command to remove the currently loaded model from the {\bf G-Shell}. A new model can then be loaded via the {\tt ndf\_load} command (see \href{../tutorial1/tutorial1.tex}{Tutorial 1} for details).

\end{enumerate}

\subsection*{GENESIS Help from the Unix Command Line}
Several options are recognized when starting GENESIS. They include, ``{\tt --help}'', ``{\tt --verbose}'', and ``{\tt --version}''. For example, typing
\begin{verbatim}
    $ genesis-g3 --help
\end{verbatim}
returns a list of options that can be used when starting the {\bf G-Shell}.
\begin{verbatim}
    options:
        --help     print usage information.
        --verbose  set verbosity level ( . . . ).
        --version  give version information.
\end{verbatim}
The four arguments to the ``{\tt --verbose}'' option flag (``{\tt errors}'', ``{\tt warnings}'', '`{\tt information}'', and ``{\tt debug}'') generate increasing levels of output by the {\bf G-Shell}. They may be invoked at startup in the following way, for example,
\begin{verbatim}
    $ genesis-g3 --verbose warnings
\end{verbatim}
Note that ``{\tt warnings}'' defines the default level of output.

\subsection*{Controlling Output from the GENESIS Shell}

\subsubsection*{The {\tt verbose} Commands}

In its default state, with the exception of error messages, the {\bf G-Shell} generates minimal output. This means that in the default state, if output occurs then something is wrong.

The amount of output generated by the {\bf G-Shell} is controlled by the {\tt set\_verbose} option.  This option recognizes several arguments that generate increasing amounts of output. They include the default setting {\tt errors} which displays only error state messages, also {\tt warnings} which displays warning and error messages, {\tt information} which displays information, warning, and error messages, and the most prolific, {\tt debug} which is used for software development and also generates maintenance errors. To use the {\tt set\_verbose} option in the {\bf G-Shell}, enter, e.g.
\begin{verbatim}
    genesis > set_verbose debug
\end{verbatim}
To return the shell to its default {\tt verbose} state, just enter ``{\tt set\_verbose warnings}''.  To check the state of the {\tt verbose} flag, enter
\begin{verbatim}
    genesis > show_verbose
        verbose_level: warnings
\end{verbatim}

\subsection*{The {\tt help} and {\tt list} Queries}
The {\bf G-Shell} recognizes a {\tt help} query. In the absence of an argument, i.e. just entering ``{\tt help}'', an error message is generated that contains the recognized sub-topics, e.g.
\begin{verbatim}
    genesis > help
        synopsis: help 
        synopsis:  must be one of commands, components, variables, libraries
\end{verbatim}
Similarly, in the absence of an argument the {\tt list} query generates an error message that contains the recognized argument types:
\begin{verbatim}
    genesis > list
    synopsis: list
    synopsis: must be one of commands, components, functions,
              inputclass_templates, inputclasses, physical,
              sections, structure, verbose
\end{verbatim}
We can then find help on a specific topic, for example, {\tt command}
\begin{verbatim}
    genesis > help command
    synopsis: list
    description: help on a specific command
    synopsis: 'help command '
    all commands:
\end{verbatim}
To find help on a specific sub-topic the {\tt list} query can be used to find, for example, the commands available to the {\bf G-Shell}, e.g.
\begin{verbatim}
    genesis > list commands 
        all commands:
          - ce
          - check
          - component_load
          - create
          - delete
          - echo
          - exit
          - explore
          - help
          - input_add
          - input_delete
          - input_show
          - inputclass_add
          - inputclass_delete
          - inputclass_show
          - inputclass_template_show
          - library_show
          - list
          - list_elements
          - model_parameter_add
          - model_parameter_show
          - model_state_load
          - model_state_save
          - morphology_list_spine_heads
          - morphology_summarize
          - ndf_load
          - ndf_save
          - npl_load
          - npy_load
          - output_add
          - parameter_scaled_show
          - parameter_show
          - pwe
          - py_diagnose
          - pynn_load
          - querymachine
          - quit
          - reset
          - run
          - runtime_parameter_add
          - runtime_parameter_delete
          - runtime_parameters_show
          - set_verbose
          - sh
          - show_global_time
          - show_verbose
          - sli_listcommands
          - sli_listobjects
          - sli_load
          - sli_run
          - sli_script
          - ssp_load
          - ssp_save
          - swc_load
          - tabulate
          - xml_load
          - xml_save
\end{verbatim}
We can then obtain help on a specific command with, for example
\begin{verbatim}
    genesis > help command output_add
        description: add a variable to the output file.
        synopsis: add_output
\end{verbatim}

\end{document}