\documentclass[12pt]{article}
\usepackage{verbatim}
\usepackage[dvips]{epsfig}
\usepackage{color}
\usepackage{url}
\usepackage[colorlinks=true]{hyperref}

\begin{document}

\section*{GENESIS: Documentation}

{\bf Related Documentation:}
% start: userdocs-tag-replace-items related-do-nothing
% end: userdocs-tag-replace-items related-do-nothing

\section*{Developer Tools}

Documentation of the tools available for GENESIS developers are provided by the following links:

\begin{itemize}
   \item[]\href{../developer-package/developer-package.tex}{\it DeveloperPackage:} Provides developer utilities that comply with GENESIS development standards.
   \item[]\href{../autogen/autogen.tex}{\it autogen:} Part of the GENESIS build system used by the {\it DeveloperPackage}.
   \item[]\href{../build-debian/build-debian.tex}{\bf Build\,a\,Debian\,Package:} Guide for building a Debian package for a GENESIS release.
   \item[]\href{../neurospaces-tester/neurospaces-tester.tex}{\bf Neurospaces\,Tester:} Provides a general purpose framework for regressing testing. Includes examples of how to prepare it for your system. 
   \item[]\href{../neurospaces-cron/neurospaces-cron.tex}{\it neurospaces-cron:} Performs sanity checks for communicating with a repository, system installation, and runs tests to check that software packages are properly working.
   \item[]\href{../userdocs-cron/userdocs-cron.tex}{\it userdocs\_cron:} Part of the {\it userdocs} package automates the (re)building of the GENESIS Documentation System.
   \item[]\href{../version-control/version-control.tex}{\bf Version\,Control:} Automates many tedious and error-prone tasks in group software development.
   \item[]\href{../cxref/cxref.tex}{\bf Xrefractory:} Browse and restructure source code and convert it to browsable html pages. 

\end{itemize}

\end{document}
