\documentclass[12pt]{article}
\usepackage[dvips]{epsfig}
\usepackage{color}
\usepackage{url}
\usepackage[colorlinks=true]{hyperref}

\begin{document}

\section*{GENESIS: Documentation}

\section*{Experiment: A Library of Stimulation and Recording Objects}

The Experiment package delivers a library of stimulation and recording
objects.

\subsection*{Features}

For stimulation protocols:
\begin{itemize}
\item Can be driven from C, Perl, SSP.
\item Implements voltage clamp and current clamp protocols.
\item Allows pulsed command protocols.
\item Allows command voltages or current to be read from a file.
\end{itemize} 

For recording:
\begin{itemize}
\item Can be driven from C, Perl, SSP.
\item Allows to record any computed variable to an ascii file.
\item Allows to record spike trains.
\end{itemize} 

\subsection*{Extensions}
\begin{itemize}
\item
  \href{../genesis-add-object-solver/genesis-add-object-solver.tex}{\bf
    Create and Add New Solver Object:} Shows by example how to add a
  new simulation object and integrate the modified component with
  GENESIS.
\item
  \href{../genesis-add-swigbinding-heccer/genesis-add-swigbinding-heccer.tex}{Add
    a SWIG binding to {\bf HECCER:}} Shows by example how to implement
  the necessary bindings to make a
  \href{../simulation-objects/simulation-objects.tex}{\bf
    Simulation\,Object} callable from Perl using SWIG and integrate it
  with \href{../ssp/ssp.tex}.
\end{itemize}
\end{document}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
