\documentclass[12pt]{article}
\usepackage{verbatim}
\usepackage[dvips]{epsfig}
\usepackage{color}
\usepackage{url}
\usepackage[colorlinks=true]{hyperref}

\begin{document}

\section*{GENESIS: Documentation}

{\bf Related Documentation:}
% start: userdocs-tag-replace-items related-do-nothing
% end: userdocs-tag-replace-items related-do-nothing

\section*{GENESIS Developers Meeting}

\subsection*{San Antonio October 28-30, 2009}

\subsection*{Locations}
\paragraph{\bf Wednesday-Thursday:} UTSA Biotechnology, Sciences, and Engineering Building Rm. 2.210.
\paragraph{\bf Friday:} UTHSCSA Research Imaging Institute (North Greehy Campus, McDermott Bldg) Library Rm. 2.610.

\subsection*{\underline{Tuesday October 27}}
\paragraph{\bf Evening:} Dinner ~7pm County Line BBQ off I10. \\
Call Dave Beeman for time: 720-270-6865.

\subsection*{\underline{Wednesday October 28}}
\subsubsection*{Theme: Model Visualization and Analysis with GENESIS}
\subsubsection*{Morning (9-12am):}
\begin{itemize}
   \item[]{\bf Hugo:} History of GENESIS $->$ problem statement.
   \item[]{\bf Allan:} The CBI federated software architecture.
   \item[]{\bf Hugo:} GENESIS G-Shell and Neurospaces Studio.
   \item[]{\bf Mando:} G-Tube, the GENESIS GUI.
\end{itemize}

\subsubsection*{Afternoon (1-5pm):}
\begin{itemize}
   \item[]{\bf Dave Beeman:} Overview of auditory cortex model. \\
      Outline network model visualization and analysis requirements.
   \item[]{\bf David Senseman:} Turtle visual cortex model, motor neuron modeling/analysis. \\
      Outline single cell and network model visualization/analysis requirements.
  \item[]{\bf Kay Robbins:} Overview of DAVIS. \\
      Outline of DAVIS functionality. Model visualization/analysis requirements.
\end{itemize}
{\bf Group Discussion Topic:} What graphical tools should G-3 provide for analysis of activity in a network model?

\subsection*{\underline{Thursday October 29}}
\subsubsection*{\bf Morning (9-12pm):}
\subsubsection*{\bf Theme: The GENESIS Publication Paradigm.}

\begin{itemize}
   \item[]{\bf Hugo:} Overview of the GENESIS Publication paradigm.
   \item[]{\bf Allan:} The GENESIS Documentation System.
\end{itemize}
\paragraph{\bf Group Discussion Topic:} (1) Requirements and implementation of the GENESIS publication paradigm. (2) Development of an outline/workflow for the GENESIS Publication paradigm.

\subsubsection*{Afternoon (1-4pm):}
\subsubsection*{Theme: GENESIS alpha release and beyond.}
\begin{itemize}
   \item[]Report on progress towards an alpha release.
   \item[]Scheduling of the alpha release.
   \item[]Choice of alpha testers.
   \item[]Alpha tester reporting requirements.
\end{itemize}
\paragraph{\bf Group Discussion Topic:} Criteria for ``readiness" of alpha, beta, and initial 3.0 releases in terms of user expectations and needs.

\subsection*{\underline{Friday October 30}}
\paragraph{\bf Morning (11-1pm):}
\paragraph{\bf Theme: Auditory system meeting.}

Attendees from UTSA and RII.

\paragraph{\bf Afternoon (3-5pm):}
Final discussion and conclusions.

\end{document}
