\documentclass[12pt]{article}
\usepackage{verbatim}
\usepackage[dvips]{epsfig}
\usepackage{color}
\usepackage{url}
\usepackage[colorlinks=true]{hyperref}

\begin{document}

\section*{GENESIS: Documentation}

{\bf Related Documentation:}
% start: userdocs-tag-replace-items related-do-nothing
% end: userdocs-tag-replace-items related-do-nothing

\section*{The GENESIS System}

\subsection*{\bf repo-genesis3.cbi.utsa.edu}

\begin{itemize}

\item {\bf monotone repository:} Serves the \href{http://www.monotone.ca/}{\bf monotone} repositories for the GENESIS project. Uses a port for each package to be served over the Internet.

\item {\bf \href{../neurospaces-tester/neurospaces-tester.tex}{Automated tester}:} A {\it cronjob} which performs a test of all packages available over the repository.  It takes at least 45 minutes to complete the tests. To serve tester output over the internet a directory owned by the non-privileged user that the {\it cronjob} runs as must be configured to be served over the internet.

\item {\bf Xrefactory cross references:} A {\it cronjob} which builds a set of html pages built in \href{http://www.xref-tech.com/xrefactory/main.html}{\bf Xrefactory} that lists function references.  Requires Xrefactory with a configuration file that has been specifically configured for the GENESIS project directory tree. 

\end{itemize}

\subsection*{\bf darwin.cbi.utsa.edu}

\begin{itemize}

\item {\bf genesis-sim.org website:} The website for GENESIS uses the \href{http://drupal.org/}{\bf Drupal CMS} which requires \href{http://www.php.net/}{\bf php5} and a \href{http://www.mysql.com/}{\bf MYSQL} database.

\item {\bf Automated user documentation:} Builds the \href{../documentation-overview/documentation-overview.tex}{\bf GENESIS Documentation System} and puts it on a link available from the GENESIS website.  Uses {\it htlatex} and is very resource intensive.  See \href{../userdocs-cron/userdocs-cron.tex}{\it userdocs-cron}.

\end{itemize}

\end{document}
