\documentclass[12pt]{article}
\usepackage{verbatim}
\usepackage[dvips]{epsfig}
\usepackage{color}
\usepackage{url}
\usepackage[colorlinks=true]{hyperref}

\begin{document}

\section*{GENESIS: Documentation}

{\bf Related Documentation:}
% start: userdocs-tag-replace-items related-do-nothing
% end: userdocs-tag-replace-items related-do-nothing

\section*{De Schutter: Purkinje Cell Model}

\subsection*{VARIABILITY IN PURKINJE CELL RESPONSE PROPERTIES}

In slice preparations, different Purkinje cells often have quitedifferent firing patterns, especially as concerns the patternof interacting somatic and dendritic spikes (Fig.\,11 in \,\cite{R:1980ly}) 
and the slope of the $f-I$ curve.However, a compartmental model is deterministic, i.e., alwaysproducing the same output for a given input. Variabilityin response properties comes about only as a result ofvarying parameters in the model.
In the case of the current model, we found that all of thereported variations in firing patterns could be obtained bysimply changing the density of K$^+$ conductances in thesoma and the main dendrite of the model. Figures\,\href{../pub-purkinje-deschutter1-fig-3/pub-purkinje-deschutter1-fig-3.tex}{\bf\,3} and \href{../pub-purkinje-deschutter1-fig-4/pub-purkinje-deschutter1-fig-4.tex}{\bf\,4}compare the firing of a model with low K$^+$ conductance(PM9) with a model with high K$^+$ conductance (PM 10).Although these models were similar in all responses describedso far, they showed richly different patterns of somatic firing that encompassed most of the observed ones.
Compare, for example, the somatic responses toward theend of the current injections in Figs.\,\href{../pub-purkinje-deschutter1-fig-3/pub-purkinje-deschutter1-fig-3.tex}{\bf\,3{\it B} and {\it C}}, and \href{../pub-purkinje-deschutter1-fig-4/pub-purkinje-deschutter1-fig-4.tex}{\bf\,4{\it D}}and after the current step in Fig.\,\href{../pub-purkinje-deschutter1-fig-3/pub-purkinje-deschutter1-fig-3.tex}{\bf\,3{\it D}}. The higher K$^+$ channeldensities in model PM 10 made the soma also less excitable,resulting in a shallower $f-I$ curve (\href{../pub-purkinje-deschutter1-fig-6/pub-purkinje-deschutter1-fig-6.tex}{\bf Fig. 6{\it A}}).

\subsection*{RESPONSE VARIABILITY}

Although any particular set of parametersin the model generated an identical (deterministic)output, we have also found that slight variations inparameters could produce the kinds of subtle variationsseen in Purkinje cell recordings. Thus different levels ofcurrent injection, small changes in the densities of outwardcurrents (PM9 versus PM10), or slight changes in morphologygenerated subtle changes in model output. Under theseconditions the Purkinje cell model responded generally inthe same way but also showed small variations in the detailsof its responses (e.g., in the sequence of action potentials).We believe this variability in the model is important, becausethe specific objective of this effort was to represent theentire population of Purkinje cells rather than just one individualcell\,\cite{Bower:1992vn}.
One of the variable aspects of Purkinje cells that has beenpreviously described involves the details of the $f-I$ curve\,\cite{R:1980ly}. Further, this curve canchange during long recordings of the same cell (D. Jaeger,personal communication). It is interesting that changes inthe density of the delayed rectifier and noninactivating K$^+$channels in the model alone could cause a lot of this variability,as can be seen by comparing \href{../pub-purkinje-deschutter1-fig-3/pub-purkinje-deschutter1-fig-3.tex}{\bf Fig.\,3} with \href{../pub-purkinje-deschutter1-fig-4/pub-purkinje-deschutter1-fig-4.tex}{\bf Fig. 4} and inthe $f-I$ curves of \href{../pub-purkinje-deschutter1-fig-6/pub-purkinje-deschutter1-fig-6.tex}{\bf Fig. 6{\it A}}. The results from patch-clamp recordingsdemonstrating that Purkinje cell Kdr channels areunder metabolic control by protein kinase C, which attenuatesKdr current\,\cite{Linden:1992ys} could provide onemechanism for short term changes inf-1 relationships. Further,our finding that somatic action potentials only repolarizedcompletely when Kdr channels were added to themain dendrite showed that the Kdr channel also controlsthe coupling between the soma and more distal dendritethat may influence thesef-I relationships. This distributionof Kdr channels matches data obtained with voltage-sensitivedye imaging, where a decoupling between the soma andthe more distal dendrite could be removed by blocking K$^+$channels\,\cite{Knopfel:1990zr}.

\bibliographystyle{plain}
\bibliography{../tex/bib/g3-refs.bib}

\end{document}
