\documentclass[12pt]{article}
\usepackage{verbatim,}
\usepackage[dvips]{epsfig}
\usepackage{color}
\usepackage{url}
\usepackage[colorlinks=true]{hyperref}

\begin{document}

\section*{GENESIS: Documentation}

{\bf Related Documentation:}
% start: userdocs-tag-replace-items related-do-nothing
% end: userdocs-tag-replace-items related-do-nothing

\section*{De Schutter \& Bower Purkinje Cell Model Lineages}

Here, we give the reported lineage of the various components in the De Schutter \& Bower Purkinje cell model:
\begin{itemize}
\item De Schutter E \& Bower JM (1994) An active membrane model of the cerebellar Purkinje cell I. Simulation of current clamp in slice. {\it Journal of Nerurophysiology}. {\bf 71}: 375--400.
\end{itemize}

\subsection*{Morphology}

\subsubsection*{Passive}

\begin{itemize}
   \item Llin\'as R \& Nicholson C (1976) Reversal properties of climbing fiber pontential in cat Purkinje cells: An example of a distributed synapse. {\it Journal of Neurophysiology}. {\bf 39}: 311-323.
   
   \item Rapp M, Segev I \& Yarom Y (1994) Physiology, morphology and detailed passive models of guinea-pig cerebellar Purkinje cells. {\it Journal of Physiology} (Lond.). {\bf 474}: 101--118.
   \begin{enumerate}
\item Purkinje cells (PCs) from guinea-pig cerebellar slices were physiologically characterizedusing intracellular techniques. Extracellular caesium ions were used to linearize themembrane properties of PCs near the resting potential. Under these conditions the averageinput resistance, $R_N$, was 29 M½, the average system time constant, $\tau_0$, was 82\,ms andthe average cable length, $L_N$, was 0.59.\item Three PCs were fully reconstructed following physiological measurements and stainingwith horseradish peroxidase. Assuming that each spine has an area of 1$\mu$m$^2$ and that thespine density over the spiny dendrites is ten spines per micrometre length, the totalmembrane area of each PC is $\sim$150,000 $\mu$m$^2$, of which $\sim$100,000 $\mu$m$^2$ is in the spines.\item Detailed passive cable and compartmental models were built for each of the three reconstructedPCs. Computational methods were devised to incorporate globally the hugenumber of spines into these models. In all three cells the models predict that the specificmembrane resistivity, $R_m$ of the soma is much lower than the dendritic $R_m$ (Å500 andÅ100,000 $\Omega$cm$^2$ respectively). The specific membrane capacitance, $C_m$, is estimated to be1.5--2 $\mu$Fcm$^{-2}$ and the specific cytoplasm resistivity, $R_l$, is 250 $\Omega$cm.\item The average cable length of the dendrites according to the model is 0.13$\lambda$, suggesting thatunder caesium conditions PCs are electrically very compact. Brief somatic spikes, however,are expected to attenuate 30-fold when spreading passively into the dendritic terminals.A simulated 200\,Hz train of fast, 90\,mV somatic spikes produced a smooth 12\,mV steadydepolarization at the dendritic terminals.\item A transient synaptic conductance increase, with a 1\,nS peak at 0.5 ms and a driving forceof 60\,mV, is expected to produce Å20 mV peak depolarization at the spine head membrane.This EPSP then attenuates between 200- and 900-fold into the soma. Approximately 800randomly distributed and synchronously activated spiny inputs are required to fire thesoma.\item The passive model of the PC predicts a poor resolution of the spatio-temporal pattern ofthe parallel fibre input. An equally sized, randomly distributed group of 11\,\% of theparallel fibres, activated within a time window of a few milliseconds, would result inapproximately the same composite EPSP at the soma.
   \end{enumerate}
   
   \item Shelton DP (1985) Membrane resistivity estimated for the Purkinje neuron by means of a passive computer model. {\it Neuroscience}. {\bf 14}: 111--131.
   
\end{itemize}
   
\subsubsection*{Active}

\begin{itemize}
   \item Pellionisz \& Llin\'as (1977)
   \item Bush \& Sejnowski (1991)
   \item De Schutter \& Bower (1994)
   \begin{enumerate}
\item A detailed compartmental model of a cerebellar Purkinje
   cell with active dendritic membrane was constructed. The modelwas based on anatomic reconstructions of single Purkinje cells andincluded 10 different types of voltage-dependent channels describedby Hodgkin-Huxley equations, derived from Purkinje cellspecificvoltage-clamp data where available. These channels includeda fast and persistent Na$^+$ channel, three voltage-dependentK$^+$ channels, T-type and P-type Ca$^{2+}$ channels, and two types ofCa$^{2+}$-activated K$^+$ channels.\item The ionic channels were distributed differentially over threezones of the model, with Na$^+$ channels in the soma, fast K$^+$ channelsin the soma and main dendrite, and Ca$^{2+}$ channels and Ca$^{2+}$-activated K$^+$ channels in the entire dendrite. Channel densities inthe model were varied until it could reproduce Purkinje cell responsesto current injections in the soma or dendrite, as observedin slice recordings.\item As in real Purkinje cells, the model generated two types ofspiking behavior. In response to small current injections themodel fired exclusively fast somatic spikes. These somatic spikeswere caused by Na$^+$ channels and repolarized by the delayed rectifier.When higher-amplitude current injections were given, sodiumspiking increased in frequency until the model generatedlarge dendritic Ca$^{2+}$ spikes. Analysis of membrane currents underlyingthis behavior showed that these Ca$^{2+}$ spikes were caused bythe P-type Ca$^{2+}$ channel and repolarized by the BK-type Ca$^{2+}$-activatedK$^+$ channel. As in pharmacological blocking experiments,removal of Na$^+$ channels abolished the fast spikes and removal ofCa$^{2+}$ channels removed Ca$^{2+}$ spiking.\item In addition to spiking behavior, the model also producedslow plateau potentials in both the dendrite and soma. Theselonger-duration potentials occurred in response to both short andprolonged current steps. Analysis of the model demonstrated thatthe plateau potentials in the soma were caused by the windowcurrent component of the fast Na$^+$ current, which was muchlarger than the current through the persistent Na$^+$ channels.Plateau potentials in the dendrite were carried by the same P-typeCa$^{2+}$ channel that was also responsible for Ca$^{2+}$ spike generation.The P channel could participate in both model functions becauseof the low-threshold K$_2$-type Ca$^{2+}$-activated K$^+$ channel, whichdynamically changed the threshold for dendritic spike generationthrough a negative feedback loop with the activation kinetics ofthe P-type Ca$^{2+}$ channel.\item These model responses were robust to changes in the densitiesof all of the ionic channels. For most of the channels, modifyingtheir densities by factors of 22 resulted only in left or rightshifts of the frequency-current curve. However, changes of $>$20\%to the amount of P-type Ca$^{2+}$ channels or of one of the Ca$^{2+}$-activatedK$^+$ channels in the model either suppressed dendritic spikesor caused the model to always fire Ca$^{2+}$ spikes. Modeling resultswere also robust to variations in Purkinje cell morphology. Wesimulated models of two other anatomically reconstructed Purkinjecells with the same channel distributions and got similarresponses to current injections.
\item The model was used to compare the electrotonic length ofthe Purkinje cell in the presence and absence of active dendriticconductances. The electrotonic distance from soma to the tip ofthe most distal dendrite increased from 0.57 X in a passive modelto 0.95 X in a quiet model with active membrane. During a dendriticspike generated by current injection the distance increasedeven more, to 1.57 X.\item Finally, the model was used to study the probable accuracyof experimental voltage-clamp data. Whole-cell patch-clamp conditionswere simulated by blocking most of the K$^+$ currents in themodel. The increased electrotonic length due to the active dendriticmembrane caused space clamp to fail, resulting in membranepotentials in proximal and distal dendrites that differed critically
from the holding potential in the soma.
\end{enumerate}
\end{itemize}

\subsection*{Channels}

\begin{itemize}

\item {\bf Fast sodium current ($Na_F$):}
   \begin{itemize}
      \item Hodgkin AL \& Huxley AF (1952) A quantitative description of membrane current and its application to conduction and excitation in nerve. {\it Journal of Physiology} (Lond.). {\bf 117}: 500--544.
      \begin{quote}
       This article concludes a series of papers concerned with the flow of electriccurrent through the surface membrane of a giant nerve fibre (Hodgkin,Huxley \& Katz, 1952; Hodgkin \& Huxley, 1952 a-c). Its general object is todiscu the results of the preceding papers (Part I), to put them intomathematical form (Part II) and to show that they will account for conductionand excitation in quantitative terms (Part III).
      \end{quote}
      
      \item G\"ahwiler BH \& Llano I (1989) Sodium and potassium conductances in somatic membranes of rat Purkinje cells from organotypic cerebellar cultures. {\it Journal of Physiology} (Lond.). {\bf 417:} 105--122.
      \begin{enumerate}
         \item The somatic voltage-gated conductances of Purkinje cells in organotypiccultures (Giihwiler, 1981) were studied using the outside-out patch recordingconfiguration of the patch-clamp technique (Hamill, Marty, Neher, Sakmann \&Sigworth, 1981).         \item When activated by step depolarizations, the tetrodotoxin-sensitive voltagedependentNa+ current presented two distinct phases: an initial surge of inwardcurrent fluctuations which activates rapidly upon pulse onset and decays within20-40\,ms, and a later phase in which discrete bursts of single-channel activity areinterspersed with silent periods.         \item Ensemble fluctuation analysis of the current fluctuations during the early phaseof the Na$^+$ current and measurements of single channels during both early and latephases indicate that a single type of Na$^+$ channel can account for both phases of theNa$^+$ current. This channel has an elementary current amplitude of -2\,pA at-40\,mV. This amplitude did not vary significantly between -60 and -20\,mV. Themean open time depended on membrane potential, increasing by a factor of threebetween -60 and -20\,mV.         \item The early component of the Na$^+$ current activated at a threshold of -60\,mVand reached its maximum amplitude at - 20, mid-point for the activation curvebeing -40\,mV. Times-to-peak current decreased with membrane potential, from3-5\,ms at -60\,mV to 0-3\,ms at 0\,mV. The decay phase of the current presented twoexponential components, with time constants of 1-5 and 10\,ms at -40\,mV. Thesteady-state inactivation curve had a mid-point at -75\,mV.         \item The late component of the Na$^+$ current was observed in the voltage range from-60 to -20\,mV, with a maximum at -40\,mV. Its maximum amplitudecorresponded to approximately 1-7\,\% of the peak amplitude of the early component.         \item Macroscopic potassium currents were observed upon step depolarizations abovea threshold of -30\,mV. The currents activated in a voltage-dependent fashion,times-to-peak decreasing with depolarization, and partially inactivated during 40\,ms
         depolarizing steps. Peak current amplitudes at any given membrane potential weredecreased by depolarizing the holding potential. The macroscopic properties of theK$^+$ current varied from patch to patch.         \item Two types of single-channel K$^+$ currents were observed during steady-statedepolarizations. The unitary current amplitudes were 2-7 and 10-4\,pA at\,30 mV,corresponding to chord conductances of 28 and 90\,pS respectively. The 28\,pS channelwas observed as well upon step depolarizations, the time course of activation for theresulting averaged currents being voltage dependent. Both 28 and 90\,pS channelswere completely inhibited by external application of 1\,mM tetraethylammoniumchloride.
      \end{enumerate}
      
      \item Hirano T \& Hagiwara S (1989) Kinetics and distribution of voltage-gated Ca, Na, and K channels on the somata of rat cerebellar Purkinje cells. {\it Pfl\"ugers Archiv}. {\bf 413}: 463--469.
      \begin{quote}
      Voltage gated ion channels on the somatic membraneof rat cerebellar Purkinje cells were studied in dissociatedcell culture with the combination of cell-attachedand whole-cell variation of patch clamp technique. Themethod enables us to record local somatic membrane currentunder an improved space clamp condition. Transient (fast-inactivating)and steady (slow-inactivating) Ca channel currents,Na current, transient (fast-inactivating) and steady(slow-inactivating) K currents, were observed. Transient andsteady Ca channel currents were activated at test potentialsmore positive than -40\,mV and -20\,mV, respectively (in50\,mM external Ba). The transient current inactivated witha half-decay time of 10-30\,ms during maintaineddepolarizing pulses, while the steady current showed relativelylittle inactivation. Na current was activated at morepositive potentials than -60\,mV, and inactivated with ahalf-decay time of less than 5\,ms. Transient and steady Koutward currents were recorded at more positive potentialthan - 20\,mV and - 40\,mV, respectively. The transient currentinactivated with a half-decay time of 2-8\,ms. Ca, Naand K channels showed different patterns of distribution onthe somatic membrane. Steady Ca channels tended to clustercompared with Na or K channels.
      \end{quote}
   \end{itemize}

\item {\bf Persistent sodium current ($Na_P$):}

\begin{itemize}

   \item French CR, Sah P, Buckett KJ \& Gage P (1990) A voltage-dependent persistent sodium current in mammalian hippocampal neurons. {\it Journal of General Physiology}. {\bf 95}: 1139--1157.
   \begin{quote}
   Currents generated by depolarizing voltage pulses were recorded inneurons from the pyramidal cell layer of the CA1 region of rat or guinea pig hippocampuswith single electrode voltage-clamp or tight-seal whole-cell voltageclamptechniques. In neurons in situ in slices, and in dissociated neurons, subtractionof currents generated by identical depolarizing voltage pulses before and afterexposure to tetrodotoxin revealed a small, persistent current after the transientcurrent. These currents could also be recorded directly in dissociated neurons inwhich other ionic currents were effectively suppressed. It was concluded that thepersistent current was carded by sodium ions because it was blocked by TIX,decreased in amplitude when extraceUular sodium concentration was reduced, andwas not blocked by cadmium. The amplitude of the persistent sodium current variedwith clamp potential, being detectable at potentials as negative as -70\,mV andreaching a maximum at $\sim$-40\,mV. The maximum amplitude at -40\,mV in 21cells in slices was -0.34\,$\pm$\,0.05 nA (mean\,$\pm$\,1 SEM) and -0.21\,$\pm$\,0.05 nA in 10dissociated neurons. Persistent sodium conductance increased sigmoidally with apotential between -70 and -30\,mV and could be fitted with the Boltzmann equation,$g = g_{max}\{1 + exp[(V' - V)/k)]\}$. The average $g_{max}$, was 7.8\,$\pm$\,1.1\,nS in the 21neurons in slices and 4.4\,$\pm$\,1.6\,nS in the 10 dissociated cells that had lost theirprocesses indicating that the channels responsible are probably most denselyaggregated on or close to the soma. The half-maximum conductance occurredclose to -50\,mV, both in neurons in slices and in dissociated neurons, and theslope factor ($k$) was 5-9\,mV. The persistent sodium current was much more resistantto inactivation by depolarization than the transient current and could berecorded at $>$50\,\% of its normal amplitude when the transient current was completelyinactivated.Because the persistent sodium current activates at potentials close to the restingmembrane potential and is very resistant to inactivation, it probably plays animportant role in the repetitive firing of action potentials caused by prolonged
depolarizations such as those that occur during barrages of synaptic inputs intothese cells.
   \end{quote}
   
   \item Kay AR \& Wong RKS (1987) Calcium current activation kinetics in isolated pyramidal neurons of the CA1 region of the mature guinea-pig hippocampus. {\it Journal of Physiology} (Lond.). {\bf 392}: 603-616.
   \begin{enumerate}
      \item Neurones were isolated from the CAI region of the guinea-pig hippocampus andsubjected to the whole-cell mode of voltage clamping, to determine the kinetics ofvoltage-gated Ca$^{2+}$ channel activation.      \item Isolated neurones had an abbreviated morphology, having lost most of thedistal dendritic tree during the isolation procedure. The electrical compactness of thecells facilitates voltage clamp analysis.      \item Block of sodium and potassium currents revealed a persistent current activatedon depolarization above -40\,mV, which inactivated slowly when the intracellularmedium contained EGTA. The current was blocked by Co$^{2+}$ and Cd$^{2+}$, augmented byincreases in Ca$^{2+}$ and could be carried by Ba$^{2+}$, suggesting that the current is borneby Ca$^{2+}$.      \item Steady-state activation of the Ca$^{2+}$ current was found to be well described bythe Boltzman equation raised to the second power.      \item The open channel's current-voltage ($I-V$) relationship rectified in the inwarddirection and was consistent with the constant-field equation.      \item The kinetics of Ca$^{2+}$ current onset followed $m^2$ kinetics throughout the range ofits activation. Tail current kinetics were in accord with this model. A detailedHodgkin-Huxley model was derived, defining the activation of this current.      \item The kinetics of the currents observed in this regionally and morphologicallydefined class of neurones were consistent with the existence of a single kinetic classof channels.
   \end{enumerate}
\end{itemize}

\item {\bf T-type calcium current ($Ca_T$):}

\begin{itemize}
\item Gruol DL \& Deal CR (1990) Expression of calcium conductances in Purkinje neurons in culture. {\it Society for Neuroscience Abstracts.} {\bf 16}: 677.

\item Hirano T \& Hagiwara S (1989) Kinetics and distribution of voltage-gated Ca, Na, and K channels on the somata of rat cerebellar Purkinje cells. {\it Pfl\"ugers Archiv}. {\bf 413}: 463--469.
      \begin{quote}
      Voltage gated ion channels on the somatic membraneof rat cerebellar Purkinje cells were studied in dissociatedcell culture with the combination of cell-attachedand whole-cell variation of patch clamp technique. Themethod enables us to record local somatic membrane currentunder an improved space clamp condition. Transient (fast-inactivating)and steady (slow-inactivating) Ca channel currents,Na current, transient (fast-inactivating) and steady(slow-inactivating) K currents, were observed. Transient andsteady Ca channel currents were activated at test potentialsmore positive than -40\,mV and -20\,mV, respectively (in50\,mM external Ba). The transient current inactivated witha half-decay time of 10-30\,ms during maintaineddepolarizing pulses, while the steady current showed relativelylittle inactivation. Na current was activated at morepositive potentials than -60\,mV, and inactivated with ahalf-decay time of less than 5\,ms. Transient and steady Koutward currents were recorded at more positive potentialthan - 20\,mV and - 40\,mV, respectively. The transient currentinactivated with a half-decay time of 2-8\,ms. Ca, Naand K channels showed different patterns of distribution onthe somatic membrane. Steady Ca channels tended to clustercompared with Na or K channels.
      \end{quote} 

\item Kaneda M, Wakamori M, Ito M \& Akaike N (1990) Low-threshold calcium current in isolated Purkinje cell bodies of rat cerebellum. {\it Journal of Neurophysiology.} {\bf 63}: 1046--1051.

\begin{enumerate}
   \item The low- and high-threshold Ca$^{2+}$ currents were observed inPurkinje cell bodies isolated from the cerebellum of newborn (2wk old) and adult (8 wk old) rats under whole-cell clamp. Atransient Ca$^{2+}$ current (low-threshold or ``T-type'' $I_{Ca}$ was elicitedbv depolarizing step pulses to -60\,mV or more positive potentialsfrom a holding potential ($V_H$) of -100 mV. In cells dissociatedfrom newborn rats, a long-lasting Ca$^{2+}$ current (high-threshold or``L-type'' $I_{Ca}$) was also elicited by depolarizing command pulsesbeyond -30\,mV.   \item The low-threshold $I_{Ca}$ was resistant to the ``washout'' effectduring the internal perfusion. whereas the high-threshold $I_{Ca}$faded gradually with time during the continuous internal perfusion.   \item In the current-voltage ($I- V$) relationship, the low-threshold$I_{Ca}$ had a threshold potential around -60\,mV and reached themaximum inward current around -20\,mV. The activation andinactivation kinetics of the current depended on membrane potential:for a test-potential change from -60 to +40\,mV, the timeto peak of the current (activation) decreased from 31.9 to 5.0 ms,and the time constant of current decay (inactivation) decreasedfrom 78.5 to 22.9\,ms.   \item Steady-state inactivation of low-threshold $I_{Ca}$ was membrane-potential dependent, and the inactivation of the 50\,\% levelwas -79\,mV. Recovery time constant from steady-state inactivationvaried depending on the membrane potential. The time constantswere 3.3 and 2.5 s at $V_H$s of -100 and -120\,mV, respectively.   \item The low-threshold $I_{Ca}$ was inhibited by various polyvalentmetal cations in a concentration-dependent manner: the inhibitionwas in the order of La$^{3+} >>$ Zn$^{2+} >$ Cd$^{2+} >$ Ni$^{2+} >$ Co$^{2+}$.   \item Various organic CaÓ antagonists also inhibited the low-threshold$I_{Ca}$ in a concentration-dependent manner; the order ofthe inhibition was flunarizinc $>$ nicardipine $>$ D-600 $>$ diltiazem.The inhibitory potencv of nicardipine varied depending on externalCa$^{2+}$ concentration. At a concentration of 3$\times$10$^-6$\,M nicardipine,the inhibitory effect on the low-threshold $I_{Ca}$ in the bathingmedium with 2.5\,mM Ca$^{2+}$ was stronger than with 10\,mM Ca$^{2+}$.   \item We found that the pharmacological properties of low-threshold$I_{Ca}$, in cerebellar Purkinje cell bodies were similar tothose in the isolated hypothalamic neurons. but differed fromthose in the peripheral ganglion cells.

\end{enumerate}

\end{itemize}

\item {\bf P-type calcium current ($Ca_P$):}
\begin{itemize}
   \item Llin\'as RR, Sugimori M \& Cherskey B (1989) Voltage-dependent calcium conductances in mammalian neurons: The P channel. {\it Annals of the American Academy of Science.} {\bf 560}: 103--111.
   
   \item Regan LJ (1991) Voltage-dependent calcium currents in Purkinje cells from rat cerebellar vermis. {\it Journal of Neuroscience.} {\bf 11}: 2259--2269.
   \begin{quote}
   Whole-cell patch clamp recording was used to characterizecalcium currents in Purkinje cells dissociated from the cerebellarvermis of 1-3-week postnatal rats. A subset of Purkinjecells had a low-threshold, transient current similar tothe T-type current in peripheral neurons. All Purkinje cellshad a high-threshold, slowly inactivating current. Only a smallcomponent of the high-threshold current was sensitive todihydropyridine (DHP) antagonists or to the dihydropyridineagonist BAY K8644. $\omega$-Conotoxin had very little effect onthe high-threshold current. The results suggest that thesePurkinje cells have at least three types of calcium channels:T-type channels (present in only a fraction of cells), DHP sensitiveL-type channels (contributing a small fraction ofthe high-threshold current), and a predominant type of highthresholdchannel that is pharmacologically distinct fromL-type and N-type channels characterized in peripheral neurons.
   \end{quote}

   \item Usowics MM, Sugimori M, Chersky B \& Llin\'as RR (1992) Characterization of P-type calcium channels in cerebellar Purkinje cells. {\it Society for Neuroscience Abstracts.} {\bf 18}: 974.
   
   \item Usowics MM, Sugimori M, Chersky B \& Llin\'as R (1992) P-type calcium channels in the somata and dendrites of adult cerebellar Purkinje cells. {\it Neuron.} {\bf 9}:1185--1199.
   \begin{quote}
The pharmacological and single-channel properties of Ca$^{2+}$ channels were studied in the somata and dendrites of adult cerebellar Purkinje cells. The Ca$^{2+}$ channels were exclusively of the high threshold type: low threshold Ca$^{2+}$ channels were not found. These high threshold channels were not blocked by omega-conotoxin GVIA and were inhibited rather than activated by BAY K 8644. They were therefore pharmacologically distinct from high threshold N- and L-type channels. Funnel web spider toxin was an effective blocker. The channels opened to conductance levels of 9, 14, and 19\,pS (in 110\,mM Ba$^{2+}$). These slope conductances were in the range of those reported for N- and L-type channels. Our results are in agreement with previous reports suggesting that Ca$^{2+}$ channels in Purkinje cells can be classified as P-type channels according to their pharmacology. The results also suggest that distinctions among Ca$^{2+}$ channel types based on the single-channel conductance are not definitive.
   \end{quote}
   
\end{itemize}

\item {\bf Anomalous rectifier ($K_h$):}

\item {\bf Delayed rectifier ($K_{dr}$):}

\item {\bf Persistent potassium current ($K_m$):}

\item {\bf A current ($K_A$):}

\item {\bf Calcium-activated potassium current  ($BK$):}

\item {\bf Calcium-activated potassium current  ($K_2$):}

\item {\bf Leak current ($I_{leak}$):}

\end{itemize}

\end{document}
