\documentclass[12pt]{article}
\usepackage[dvips]{epsfig}
\usepackage{color}
%e.g.  \textcolor{red,green,blue}{text}
\usepackage{url}
\usepackage[colorlinks=true]{hyperref}

\begin{document}

\section*{GENESIS: Documentation}

{\bf Related Documentation:}
% start: userdocs-tag-replace-items related-do-nothing
% end: userdocs-tag-replace-items related-do-nothing

\section*{Reserved Words}

\begin{itemize}

\item \href{../gshell/gshell.tex}{\bf GENESIS ``Shell''}: An interactive shell provides a GENESIS ``session''. A GENESIS  {\it session} is evoked by entering ``{\tt genesis-g3}'' at a UNIX prompt. The GENESIS shell ({\bf G-Shell}) provides a unified interface and allows for convenient interaction with other software components of a given GENESIS environment.  Two introductory tutorials (\href{../tutorial1/tutorial1.tex}{\bf Tutorial\,1} and \href{../tutorial2/tutorial2.tex}{\bf Tutorial\,2}) focus on the use of GENESIS from such an interactive shell.

\item \href{../genesis-components/genesis-components.tex}{\bf GENESIS ``Component''}:  A stand-alone software module that generates specific simulator functionality by providing commands to the {\bf G-Shell}. Component functionality is evoked by GENESIS on an as-needed basis.

To generate a list of GENESIS components type ``{\tt list components}'' in the {\bf G-Shell}. To get help for a component type ``{\tt help <component name>}''. The {\it help} option gives an example of how to use a component and a one sentence description of what the component does. GENESIS software components include, the \href{../model-container/model-container.tex}{\bf Model\,Container} which loads and provides internal storage for neuronal models and can be used to perform model analysis, an equation solver (\href{../heccer/heccer.tex}{\bf Heccer}), a library of experimental protocols ({\bf Experiment}) and a simple scheduler in Perl (\href{../ssp/ssp.tex}{\bf SSP}) which coordinates and runs the GENESIS software components required to perform a simulation. We note that specific components recognize specific commands and tokens (see below).

\item {\bf GENESIS ``Command'':} Utility functions that allow operations with or on a model. Most GENESIS commands are provided by the specific components supporting a simulation. To generate a list of GENESIS commands type ``{\tt list commands}'' in the GENESIS shell. To get help for a GENESIS command type ``{\tt help <command name>}''. The {\it help} option gives an example of how to use a command and a one sentence description of what the command does.

\item {\bf GENESIS ``Token'':}  Lexical tokens are used to construct the different parts of a model. There are four sets of tokens:  {\it section}, {\it physical}, {\it function}, and {\it structure}. To generate a list of tokens type ``{\tt list tokens <set name>}''. To get help for a GENESIS token, type ``{\tt help <token name>}''. The {\it help} option gives an example of how to use a token and a one sentence description of what the token does. To learn more about the different categories of tokens, see \href{../shell-tokens/shell-tokens.tex}{\bf Shell Tokens}.

\item{\bf GENESIS ``Element'':} This is the building block used to create models under GENESIS. They are created with tokens. Once an element has been created, it can be assigned a variety of properties.

\end{itemize}

\end{document}
