\documentclass[12pt]{article}
\usepackage[dvips]{epsfig}
\usepackage{lineno}
\usepackage{color}
\usepackage{url}
\usepackage[colorlinks=true]{hyperref}

\begin{document}

\section*{GENESIS: Documentation}

{\bf Related Documentation:}

\href{../ndf-file-format/ndf-file-format.tex}{\bf The NDF File Format}

\href{../model-variables/model-variables.tex}{\bf Physical Processes and Model Variables}

\href{../ndf-procedural-description/ndf-procedural-description.tex}{\bf The NDF File Format and Procedural Model Descriptions}

% start: userdocs-tag-replace-items related-do-nothing
% end: userdocs-tag-replace-items related-do-nothing

\section*{Namespaces in the Model-Container and the Neurospaces Description Format}


The '::' notation is defined by the model component space of the
model-container (note: it is not python nor perl specific).  Neither
the gshell nor ssp nor sspy know what this notation means.

The model component space of the model-container defines the model.
Every model can be defined in a hierarchical manner.  Two examples:

1. In the G-2 version of the Purkinje cell model, the G-2 scripts
construct prototypes of channels which are then mapped onto prototypes
of dendritic sections which are then mapped onto the dendritic
morphology.

2. In the G-2 version of the cerebellar cortex network model, the G-2
scripts construct prototypes of channels which are then mapped onto
prototypes of either a single compartment Granule cell model or either
a single compartment Golgi cell model, which are then mapped onto
positions calculated by the createmap command.

The '::' supports the concept of referencing prototypes independent of
the level of the model, to facilitate the hierarchical construction of
models.

From the syntactical viewpoint the NDF file format supports
hierarchical model construction using file references with the
'IMPORT' command.  The 'IMPORT' command references a file and
associates a name with it, called the namespace.  When used in model
component references the name occuring after the '::' refers to a
namespace that is associated with a file in the IMPORTS section of an
NDF file.  For instance the snippet:

\begin{verbatim}
IMPORT
        FILE Purk_spine "segments/spines/purkinje.ndf"
END IMPORT
\end{verbatim}

defines {\tt ::Purk\_spine::} as a namespace.  After parsing every
model defined as a public model in the file
'segments/spines/purkinje.ndf' can be accessed as {\tt
  ::Purk\_spine::<model-name>}.  The NDF file {\it
  segments/spines/purkinje.ndf} defines the models {\tt Purk\_spine}
and {\tt Purk\_spine2} (both are groups of segments defining two
different variants of Purkinje cell spines), thus after parsing these
two models become accessible as {\tt ::Purk\_spine::/Purk\_spine} and
{\tt ::Purk\_spine::/Purk\_spine2}

When referencing a model component in the model component space the
notation can be understood as follows:

\begin{itemize}
\item[] {\tt /} means {\it ... who has as child ...}
\item[] {\tt ->} means {\it ... who has as parameter ...}
\item[] {\tt =} means {\it ... with the value ...}

\item[]  and then

\item[] {\tt ::} means {\it ... who has a namespace ...}
\end{itemize}

In the gshell, the command

\begin{verbatim}
ndf_load_library rscell cells/RScell-nolib2.ndf
\end{verbatim}

defines the namespace {\tt ::rscell::} and associates it with the file
{\it cells/RScell-nolib2.ndf}.  All the (public) models in this file
are now accessible from this namespace.  The statement

\begin{verbatim}
insert_alias ::rscell::/cell /two_cells/1
\end{verbatim}

creates the model component {\tt /two\_cells/1} as a reference to {\tt
  /cell} underneath the namespace {\tt ::rscell::}.

\end{document}
