\documentclass[12pt]{article}
\usepackage{verbatim}
\usepackage[dvips]{epsfig}
\usepackage{color}
\usepackage{url}
\usepackage[colorlinks=true]{hyperref}

\begin{document}

\section*{GENESIS: Documentation}

{\bf Related Documentation:}
% start: userdocs-tag-replace-items related-do-nothing
% end: userdocs-tag-replace-items related-do-nothing

\section*{De Schutter: Purkinje Cell Model}

\subsection*{Source}

De Schutter E \& Bower JM (1994) An active membrane model of the cerebellar Purkinje cell I. Simulation of current clamp in slice. {\it Journal of Nerurophysiology}. {\bf 71}: 375--400.

\noindent De Schutter E \& Bower JM (1994) An active membrane model of the cerebellar Purkinje cell II. Simulation of synaptic responses. {\it Journal of Nerurophysiology}. {\bf 71}: 375--400.

\subsection*{Abstract}

\begin{enumerate}
\item A detailed compartmental model of a cerebellar Purkinjecell with active dendritic membrane was constructed. The modelwas based on anatomic reconstructions of single Purkinje cells andincluded 10 different types of voltage-dependent channels describedby Hodgkin-Huxley equations, derived from Purkinje cell specificvoltage-clamp data where available. These channels includeda fast and persistent Na$^+$ channel, three voltage-dependentK$^+$ channels, T-type and P-type Ca$^{2+}$ channels, and two types ofCa$^{2+}$ -activated K+ channels.
\item The ionic channels were distributed differentially over threezones of the model, with Na$^+$ channels in the soma, fast K$^+$ channelsin the soma and main dendrite, and Ca$^{2+}$ channels and Ca$^{2+}$-activated K$^+$ channels in the entire dendrite. Channel densities inthe model were varied until it could reproduce Purkinje cell responsesto current injections in the soma or dendrite, as observedin slice recordings.
\item As in real Purkinje cells, the model generated two types ofspiking behavior. In response to small current injections themodel fired exclusively fast somatic spikes. These somatic spikeswere caused by Na$^+$ channels and repolarized by the delayed rectifier.When higher-amplitude current injections were given, sodiumspiking increased in frequency until the model generatedlarge dendritic Ca$^{2+}$ spikes. Analysis of membrane currents underlying this 
behavior showed that these Ca$^{2+}$ spikes were caused bythe P-type Ca$^{2+}$ channel and repolarized by the BK-type Ca$^{2+}$-activatedK$^+$ channel. As in pharmacological blocking experiments,removal of Na$^+$ channels abolished the fast spikes and removal ofCa$^{2+}$ channels removed Ca$^{2+}$ spiking.
\item In addition to spiking behavior, the model also producedslow plateau potentials in both the dendrite and soma. Theselonger-duration potentials occurred in response to both short andprolonged current steps. Analysis of the model demonstrated thatthe plateau potentials in the soma were caused by the windowcurrent component of the fast Na$^+$ current, which was muchlarger than the current through the persistent Na$^+$ channels.Plateau potentials in the dendrite were carried by the same P-typeCa$^{2+}$ channel that was also responsible for Ca$^{2+}$ spike generation.The P channel could participate in both model functions becauseof the low-threshold K2-type Ca$^{2+}$-activated K$^+$ channel, whichdynamically changed the threshold for dendritic spike generationthrough a negative feedback loop with the activation kinetics ofthe P-type Ca$^{2+}$ channel.
\item These model responses were robust to changes in the densitiesof all of the ionic channels. For most of the channels, modifyingtheir densities by factors of $\geq$2 resulted only in left or rightshifts of the frequency-current curve. However, changes of $>$20\,\%to the amount of P-type Ca$^{2+}$ channels or of one of the Ca$^{2+}$-activatedK$^+$ channels in the model either suppressed dendritic spikesor caused the model to always fire Ca$^{2+}$ spikes. Modeling resultswere also robust to variations in Purkinje cell morphology. Wesimulated models of two other anatomically reconstructed Purkinjecells with the same channel distributions and got similarresponses to current injections.

\item The model was used to compare the electrotonic length ofthe Purkinje cell in the presence and absence of active dendriticconductances. The electrotonic distance from soma to the tip ofthe most distal dendrite increased from 0.57\,$\lambda$ in a passive modelto 0.95\,$\lambda$ in a quiet model with active membrane. During a dendriticspike generated by current injection the distance increasedeven more, to 1.57\,$\lambda$.
\item Finally, the model was used to study the probable accuracyof experimental voltage-clamp data. Whole-cell patch-clamp conditionswere simulated by blocking most of the K$^+$ currents in themodel. The increased electrotonic length due to the active dendriticmembrane caused space clamp to fail, resulting in membranepotentials in proximal and distal dendrites that differed criticallyfrom the holding potential in the soma.

\item Both excitatory and inhibitory postsynaptic channels wereadded to the model to examine model responses to synapticinputs. Maximum synaptic conductance was the only parameterthat was tuned in these studies. Under theseconditions the model was capable of reproducing physiologicalrecorded responses to each of the major types of synaptic input.

\item When excitatory synapses were activated on the smoothdendrites of the model, the model generated a complex dendriticCa$^{2+}$ spike similar to that generated by climbing fiber inputs. Examinationof the model showed that activation of P-type Ca$^{2+}$channels in both the smooth and spiny dendrites augmented thedepolarization during the complex spike and that Ca$^{2+}$-activatedK$^+$ channels in the same dendritic regions determined the durationof the spike. When these synapses were activated under simulatedcurrent-clamp conditions the model also generated the characteristicdual reversal potential of the complex spike. The shapeof the dendritic complex spike could be altered by changing themaximum conductance of the climbing fiber synapse and thus theamount of Ca$^{2+}$ entering the cell.

\item To explore the background simple spike firing properties ofPurkinje cells in vivo we added excitatory ``parallel fiber'' synapsesto the spiny dendritic branches of the model. Continuousasynchronous activation of these granule cell synapses resulted inthe generation of spontaneous sodium spikes. However, very lowasynchronous input frequencies produced a highly regular, veryfast rhythm (80--120\,Hz), whereas slightly higher input frequenciesresulted in Purkinje cell bursting. Both types of activity areuncharacteristic of in vivo Purkinje cell recordings.

\item Inhibitory synapses of the sort presumably generated by stellatecells were also added to the dendritic tree. When asynchronousactivation of these inhibitory synapses was combined withcontinuous asynchronous excitatory input the model generatedsomatic action potentials in a much more stochastic pattern typicalof real Purkinje cells. Under these conditions simulated interspikeinterval distributions resembled those found in experimentalrecordings. Also, as with in vivo recordings, the model did notgenerate dendritic bursts. This was mainly due to inhibition thatsuppressed the generation of dendritic Ca$^{2+}$ spikes.

\item In the presence of asynchronous inhibition, changes in theaverage frequency of excitatory inputs modulated background simplespike firing frequencies in the natural range of Purkinje cellfiring frequencies (30--100\,Hz). This modulation was very sensitiveto small changes in the average frequency of excitatory inputs.In addition, changes in inhibitory frequency caused a parallel shiftof the relationship between excitatory input and spiking frequency.Because of the specific cerebellar circuitry, inhibitory inputsmay allow Purkinje cells to detect small fluctuations in excitatoryinput at any mean frequency of input.

\item When climbing fiber input was given in the presence ofbackground asynchronous excitatory and inhibitory inputs theshape of the complex spike in the soma was significantly affected.However, the shape of the spike in the dendrites was almost constant.This difference reflected the more variable excitability of thesoma compared with the dendrites.

\item Synchronous activation of basket cell inhibitory synapsesduring asynchronous activation of granule and stellate cell synapsesinterrupted somatic spiking. However, the hyperpolarizationcaused by the basket cell synapse did not penetrate far into thedendrite but stayed localized to the soma and main dendrite.

\item This simulation work demonstrates that a model based onvoltage-clamp data and tuned entirely on the response of Purkinjecells to current injection is capable of reproducing a wide range ofsynaptically activated responses. In the presence of continuousgranule cell excitation the model showed a stable in vivo statedifferent from the silent, resting in vitro state. Further, the modelsuggests that there may be important functional interactions betweendifferent types of synaptic inputs. In particular, it makesseveral specific predictions about the role of stellate cell inhibition.

\end{enumerate}

\end{document}
