\documentclass[12pt]{article}
\usepackage{verbatim}
\usepackage[dvips]{epsfig}
\usepackage{color}
\usepackage{url}
\usepackage[colorlinks=true]{hyperref}

\begin{document}

\section*{GENESIS: Documentation}

{\bf Related Documentation:}
% start: userdocs-tag-replace-items related-do-nothing
% end: userdocs-tag-replace-items related-do-nothing

\section*{\href{http://www.cnsorg.org/meetings/}{Computational Neuroscience Conference} (CNS)}

The following links provide access to abstracts submitted to and posters presented at CNS about the reconfiguration of GENESIS. They provide useful summaries of and background information about GENESIS.

\subsection*{Abstracts}

\begin{itemize}
\item \href{../cns07-abstract/cns07-abstract.pdf}{\bf 2007}
\item \href{../cns08a-abstract/cns08a-abstract.pdf}{\bf 2008a}
\item \href{../cns08b-abstract/cns08b-abstract.pdf}{\bf 2008b}
\item \href{../cns09-abstract/cns09-abstract.pdf}{\bf 2009}
\item \href{../cns10-publication-abstract/cns10-publication-abstract.pdf}{\bf 2010a}
\item \href{../cns10-rtxi-abstract/cns10-rtxi-abstract.pdf}{\bf 2010b}
\item \href{../cns10-cbi-utsa-uthscsa-abstract.pdf/cns10-cbi-utsa-uthscsa-abstract.pdf}{\bf 2010c}
\item \href{../cns10-pc-information-transfer-abstract.pdf/cns10-pc-information-transfer-abstract}{\bf 2010d}
\end{itemize}

\subsection*{Posters}

\begin{itemize}
\item \href{../cns07-poster/cns07-poster.pdf}{\bf 2007:} The GENESIS 3.0 Project.
\item \href{../cns08a-poster/cns08a-poster.pdf}{\bf 2008a:} The CBI Architecture for Computational Simulation of Realistic Neurons and Circuits in the GENESIS 3 Software Federation.
\item \href{../cns08b-poster/cns08b-poster.pdf}{\bf 2008b:} The Neurospaces Project Browser in the GENESIS 3 Software Federation: Design and Targets.
\item \href{../cns09-poster/cns09-poster.pdf}{\bf 2009:} Using GENESIS 3 for single neuron modeling.
\item \href{../cns10-publication-poster/cns10-publication-poster.pdf}{\bf 2010a:} Development of model-based publication for scientific communication.
\item \href{../cns10-g3-rtxi-poster/cns10-g3-rtxi-poster.pdf}{\bf 2010b:} GENESIS 3 as a convenient software integration platform: A dedicated example.
\item \href{../cns10-pc-information-transfer-poster/cns10-pc-information-transfer.pdf}{\bf 2010d:} Synaptic activity and excitability modulates information transfer in Purkinje cells: A modeling study.
\end{itemize}

\subsection*{Workshops}

\begin{itemize}
\item \href{../cns10-workshop/cns10-workshop.tex}{\bf 2010:} \href{../cns10-workshop-outline/cns10-workshop-outline.tex}{\bf Electronic\,Publication\,Workshop\,Agenda}
\end{itemize}

\end{document}
