\documentclass[12pt]{article}
\usepackage{verbatim}
\usepackage[dvips]{epsfig}
\usepackage{color}
\usepackage{url}
\usepackage[colorlinks=true]{hyperref}

\begin{document}

\section*{GENESIS: Documentation}

{\bf Related Documentation:}
% start: userdocs-tag-replace-items related-do-nothing
% end: userdocs-tag-replace-items related-do-nothing

\section*{GENESIS Developers Meeting}

GENESIS Developers Meeting
San Antonio October 28-30, 2009.

Locations
Wednesday: UTSA Biotechnology, Sciences, and Engineering Building Rm. 
Morning Session: UTSA Biotechnology, Sciences, and Engineering Building Rm. 1.110.
Afternoon Session: UTSA Biotechnology, Sciences, and Engineering Building Rm. 3.114 (to be confirmed).
Thursday: UTSA Biotechnology, Sciences, and Engineering Building Rm. 2.210.
Friday: UTHSCSA Research Imaging Institute (North Greehy Campus, McDermott Bldg) Library Rm. 2.610.

Tuesday October 27
Evening: Dinner ~7pm County Line BBQ off I10.
Call Dave Beeman for time: 720-270-6865.

Wednesday October 28
Theme: Model Visualization and Analysis with GENESIS

Morning (9-12am):
Hugo: History of GENESIS -> problem statement.

Allan: The CBI federated software architecture.

Hugo: GENESIS G-Shell and Neurospaces Studio.

Mando: G-Tube, the GENESIS GUI.

Afternoon (1-5pm):
Dave Beeman: Overview of auditory cortex model.
Outline network model visualization and analysis requirements.

David Senseman: Turtle visual cortex model and motor neuron modeling and analysis.
Outline single cell and network model visualization and analysis requirements.

Kay Robbins: Overview of DAVIS.
Outline of DAVIS functionality re: model visualization and analysis requirements.

Group Discussion
Topic: What graphical tools should G-3 provide for analysis of activity in a network model?

Thursday October 29
Morning (9-12pm):
Theme: The GENESIS Publication Paradigm

Hugo: Overview of the GENESIS Publication paradigm.

Allan: The GENESIS Documentation System.

Group Discussion
Topic: Requirements and implementation of the GENESIS publication paradigm, development of an outline/workflow for the GENESIS Publication paradigm.

Afternoon (1-4pm):
Theme: GENESIS alpha release and beyond

Report on progress towards an alpha release.
Scheduling of the alpha release.
Choice of alpha testers.
Alpha tester reporting requirements.

Group Discussion
Topic: Criteria for "readiness" of alpha, beta, and initial 3.0 releases in terms of user expectations and needs

Friday October 30

Morning (11-1pm):
Theme: Auditory system meeting

Attendees from UTSA and RII.

Afternoon (3-5pm):
Final discussion and conclusions.


\end{document}
