\documentclass[12pt]{article}
\usepackage{verbatim}
\usepackage[dvips]{epsfig}
\usepackage{color}
\usepackage{url}
\usepackage[colorlinks=true]{hyperref}

\begin{document}

\section*{GENESIS: Documentation}

{\bf Related Documentation:}
% start: userdocs-tag-replace-items related-do-nothing
% end: userdocs-tag-replace-items related-do-nothing

\section*{De Schutter: Purkinje Cell Model}

\subsection*{CALCIUM CONCENTRATION}

The distribution of Ca$^{2+}$ duringPurkinje cell activity gives clues to the underlying ionicmechanisms. This is most true for the dendrites where largeCa$^{2+}$ fluctuations were seen. The Ca$^{2+}$ concentration in thesoma remained very low (Figs. 10, E and F, and 11 A),because only CaT channels were present in the soma. Wedo not claim that our simulation ofthe Ca$^{2+}$ concentrationin the soma was realistic. However, because there were noCa$^{2+}$-activated K$^+$ channels in the soma, it did not affect
the behavior of the model and we have not tried to optimize itfurther.
During dendritic spikes, the submembrane Ca$^{2+}$ concentration 
attained a sharper peak than the membrane voltage
(Fig.\,11, {\it C} and {\it D}). It started to increase with a delay 
compared with the depolarization and the CaP channel activation, because Ca$^{2+}$ concentration under these conditions was mainly determined by the integral of Ca$^{2+}$ inflow. It
also decayed rapidly, so that it returned to baseline togetherwith the membrane potential. The Ca$^{2+}$ images in Fig. 10,{\it E} and {\it F}, show the same pattern, i.e., the Ca$^{2+}$ rise wasdelayed compared with the depolarization and showedsteeper distributions over the dendrite. This specific temporaland spatial pattern of Ca$^{2+}$ elevation restricted theactivation of Ca$^{2+}$-activated K$^+$ currents (at these elevatedconcentrations, mainly KC).

\subsection*{CALCIUM SPIKES}

As the current amplitude injected in a 
Purkinje cell increases, dendritic Ca$^{2+}$ spikes become apparentas depolarizing spike bursts in the soma. Again, themodel reproduced this behavior reasonably well (Figs.\,3, {\it B}and {\it C}, and 4, {\it C} and {\it D}). In experimental somatic recordingsthe transition between simple spikes and depolarizingspike bursts is abrupt, whereas the model often showed oneor two small bursts before a full dendritic spike becameapparent.
The transitions between the firing of simple somaticspikes and the firing of dendritic spikes causes a break in thelinearity of the frequency current ($f-1$) curve, with a second,shallower slope above this transition. Our $f-I$ curves (Fig.\,6{\it A}) 
were remarkably similar to those published by Llinasand Sugimori (\cite{R:1980ly}, their Fig.\,5). In the model, dendriticspike firing frequency remained relatively constant (16--19\,Hz 
in both models) once the threshold was crossed and wasrather insensitive to the current amplitude.

\subsection*{DENDRITIC CURRENTS AND THE CALCIUM SPIKE}

The channelscontributing to the dendritic spike operated in thesame manner in the smooth (Fig.\,11{\it C}) and spiny (Fig.\,11{\it D}) 
dendrites, but the spike itself was much bigger in thespiny dendrites because of the higher input impedance ofthe smaller dendritic branches. The dendritic spikes weregenerated by the CaP channel; the CaT channel did notplay a role in spike generation (except during a reboundspike from hyperpolarization). The dendritic spikes wererepolarized by the KC channel, which activated toward theend of the spike and deactivated rapidly afterwards. Althoughthe K2 current amplitude increased a bit during thespike, it was already quite active before the spike, when itwas a stronger outward current than the KC channel (Fig.\,11{\it C}, {\it inset}).

\subsection*{CONTROL OF DENDRITIC SPIKE GENERATION}

Control of the alternation of somatic and dendritic spiking that determinedthe overall behavior of the cell in the simulation wasa complex combination of all the events discussed so far.However, the important point is that the model clearly demonstratedthat the Ca$^{2+}$-activated K$^+$ channels interactedwith the steady, plateau-generating CaP activation as a negativefeedback loop. The K2 channel dominated this effectbecause it had a much lower threshold of Ca$^{2+}$ activationthan the KC channel, resulting in K2 currents larger thanthe KC currents between dendritic spikes (Fig.\,10{\it C}, {\it inset}).One of the clear characteristics of Purkinje cell responsesto large somatic current injections is the delay seen in activationof full-blown calcium spikes (Fig.\,3, {\it B} and {\it C}) andthen the alternation of dendritic calcium spikes and periodsof somatic action potential firing. In the model this phenomenonwas directly related to the interaction betweenthe CaP and K2 channels. Initially, depolarization resultedin a slow buildup of CaP current, which resulted in an increaseof the internal dendritic Ca$^{2+}$ concentration (e.g.,0.17\,$\mu$M at 200\,ms). This activated a large number of K2channels, effectively countering the depolarization causedby the CaP channel. As a consequence after the onset ofcurrent injection there was a fluctuation of the baselinemembrane potential in the dendrites (Fig.\,3{\it B}), but no truedendritic spikes.
During the current injection, the persistent CaP currentwas progressively reduced by $\sim$\,50\,\% because of the slowinactivation of the CaP channel until a steady state was
reached. This caused a corresponding reduction in the Ca2+concentration (e.g., 0.11\,$\mu$M between dendritic spikes at900\,ms) and less activation of the K2 channel, so that theCaP channel conductance could overcome the counteractinginfluence of the K2 channels, resulting in a full dendriticspike. Once initiated the large influx of Ca$^{2+}$ thencaused the sequence described above for the Ca$^{2+}$ spike,with the dendrite being repolarized by the KC channel.Thus it appears that the CaP channel effectively controlleddynamically the threshold of activation of dendriticspike firing through a negative feedback from the K2 channel.Because the K2 channel was sensitive to small changesin Ca$^{2+}$ concentration caused by the beginning activationof CaP channels and because the opening of K2 channelscounteracted CaP channel activation, K2 channel activationcould effectively increase the threshold for Ca$^{2+}$ spikegeneration. In other words, when the K2 current was highthe CaP channel could only cause plateaus. To generatedendritic spikes the K2 current had to be low and the CaPchannel had to activate fast. Vice versa, high CaP plateaucurrents suppressed dendritic spiking because they activatedmost of the K2 channels. This also explained the lackof full-blown dendritic spikes during the prolonged episodesof somatic depolarization with high-amplitudecurrent injections (Fig.\,3{\it D}).

\subsection*{MODELING CALCIUM CONCENTRATIONS}

For a neuron withCa$^{2+}$ activity like the Purkinje cell, the detailed modeling ofCa$^{2+}$ represents one of the biggest technical challenges.Modeling the diffusion, pumping, internal uptake and release,cytosolic buffering, etc, of Ca$^{2+}$ is a formidable computationalchallenge\,\cite{Sala:1990ys, Yamada-W:1989bs}. 
In the current version of the model weused a very simple one-shell scheme to model Ca$^{2+}$ concentration.Calcium concentration in this shell decreased witha fast exponential decay despite the fact that Ca*+ concentrationis regulated by a complex interaction of, amongothers, metabotropic receptors\,\cite{Llano:1991kx, Staub:1992zr}, 
cytoplasmic stores with IP, and ryanodine receptors\,\cite{Takei:1992ac}, 
Ca$^{2+}$ binding proteins like calbindinand parvalbumin\,\cite{Kadowaki:1993ly}, and Ca$^{2+}$inflow through the Ca$^{2+}$ channels\,\cite{Hockberger:1989ve, Lev-Ram:1992vn, Ross:339qf}. 
Clearly there is tremendous room for improvement of the model in thisregard.
Our principle reason for modeling internal Ca$^{2+}$ concentrationinvolved the regulation of conductance in the Ca$^{2+}$-activated K$^+$ channels. In this case the most relevant regionof the cell is the area immediately adjacent to the internalmembrane, which is presumably where the mechanism foractivating the K$^+$ channels operates. As presented in theRESULTS, the Ca$^{2+}$ concentration we modeled providedboth the amplitude and fast changes necessary to activatethe BK channel properly. However, at 6\,$\mu$M peak concentrations[Ca$^{2+}$] was much higher, and the change in concentrationmuch faster, than those reported for the Purkinjecell in the literature\,\cite{Hockberger:1989ve, Ross:339qf, Sugimori:1990kx, Tank:1988bh}. Onelikely explanation for this discrepancy is the time constantsinvolved in experimentally measuring Ca$^{2+}$ concentration.Each of these measurements were made with the calciumindicator fura-2, whose slow kinetics filter out fast transientsof internal calcium\,\cite{Vranesic:1991dq}.However, from the Ca$^{2+}$ sensitivity of the BK channel\,\cite{Franciolini:1988fu, Lancaster:1991ye, Reinhart1989:xe, Smart:1987mi} we know that the Ca$^{2+}$ concentrationsmust reach the micromolar range. In other neuronal systemsCa$^{2+}$ concentrations in the micromolar range\,\cite{Muller:1991cr} 
and even in the 200 to 300\,$\mu$M range\,\cite{Llinas:1992nx} 
have been reported. For these reasonswe suspect that the rapid, high-amplitude changes in Ca$^{2+}$concentration that are necessary in the model to activatethe BK channel properly may very well more accuratelyresemble the real submembrane peaks during Ca$^{2+}$ spikes.However, there is ample evidence for a slower buildup ofCa$^{2+}$ concentration during repetitive Ca$^{2+}$ spiking\,\cite{Lev-Ram:1992vn, Ross:1990oq}. 
These slower transientsare not reproduced by our model (Fig.\,11, {\it C} and {\it D}) becauseof the fast time constant of Ca$^{2+}$ removal in the shell.A more sophisticated model of Ca$^{2+}$ removal\,\cite{Sala:1990ys, Yamada-W:1989bs} will be necessaryto investigate the consequences of this slow increasein Ca$^{2+}$.

\bibliographystyle{plain}
\bibliography{../tex/bib/g3-refs.bib}

\end{document}
