\documentclass[12pt]{article}
\usepackage{verbatim}
\usepackage[dvips]{epsfig}
\usepackage{color}
\usepackage{url}
\usepackage[colorlinks=true]{hyperref}

\begin{document}

\section*{GENESIS: Documentation}

{\bf Related Documentation:}
% start: userdocs-tag-replace-items related-do-nothing
% end: userdocs-tag-replace-items related-do-nothing

\section*{De Schutter: Purkinje Cell Model}

\subsection*{Source}

De Schutter E \& Bower JM (1994) An active membrane model of the cerebellar Purkinje cell II. Simulation of synaptic responses. {\it Journal of Nerurophysiology}. {\bf 71}: 401--419.

\subsection*{Stellate Cell Synapses}

\subsubsection*{SYNAPTIC LOCATIONS}

Morphological data about stellate cell
synapse distributions on Purkinje cell dendrites are incomplete.
On the basis of EM data they seem to synapse on both small spiny
and thicker dendritic branches\,\cite{Palay:1974fk} and
in general they do not contact the innervation sites of basket cell
synapses (ibid.), but neither the densities of these synaptic contacts
nor their exact sites of termination are known. Because there
are more stellate cells than Purkinje cells\,\cite{Ito:1984uq} we assumed
that stellate cell synapses were present on all the smooth and spiny
dendritic compartments. We placed two stellate cell synaptic contacts
on the shaft of every smooth dendritic compartment and one
contact on every spiny dendritic compartment, resulting in a total
of 1,695 stellate cell synapses in the model.

\subsubsection*{SYNAPTIC PHARMACOLOGY AND KINETICS}
Stellate cell inhibition
is mediated by $\gamma$-aminobutyric acid-A (GABA$_{\mbox{A}}$) receptors\,
\cite{Gabbot:1986fk, Ito:1984uq, Llano:1991uq}. The kinetics for
this inhibitory synaptic conductance were based on recordings of
miniature inhibitory synaptic currents in pyramidal neurons of
the hippocampus\,\cite{Ropert:1990kx} with an opening time constant
of 0.9\,ms, a closing time constant of 26.5\,ms (peak at 3.2\,
ms), and a reversal potential of -80\,mV.

\subsubsection*{SYNAPTIC CONDUCTANCES}
Postsynaptic conductances on
smooth dendritic compartments had a $\bar g$ of 1.4\,mS/cm$^2$; conductances
on a spiny dendritic compartment had a $\bar g$ of 7\,mS/cm$^2$.

\subsubsection*{SYNAPTIC ACTIVATION}
Stellate cell synapses were fired asynchronously,
following a Poisson distribution around a mean frequency
of input. There was no relation between the timing of
excitatory and inhibitory inputs.

\bibliographystyle{plain}
\bibliography{../tex/bib/g3-refs}

\end{document}
