\documentclass[12pt]{article}
\usepackage{verbatim}
\usepackage[dvips]{epsfig}
\usepackage{color}
\usepackage{url}
\usepackage[colorlinks=true]{hyperref}

\begin{document}

\section*{GENESIS: Documentation}

{\bf Related Documentation:}
% start: userdocs-tag-replace-items related-do-nothing
% end: userdocs-tag-replace-items related-do-nothing

\section*{De Schutter: Purkinje Cell Model}

\subsection*{INTERACTION BETWEEN IONIC CURRENTS}

One of the principlebenefits of modeling neurons at this level of detail is thatthe interactions between different currents can be explored.All too frequently experimentalists assign very specific rolesto particular channel types without taking into account theoften complex interactions between different conductancesthat are actually responsible.
In the current model there are numerous examples of thistype of interaction. One of the most striking involves theinteraction of the noninactivating K$^+$ channels and theNa$^+$ and Ca$^{2+}$ channels responsible for the plateaus. At thesomatic level these K$^+$ conductances served to counteractthe depolarizing effect of the Na$^+$ channels, with their balancedetermining the voltage of the plateau potential(\href{../pub-purkinje-deschutter1-fig-11/pub-purkinje-deschutter1-fig-11.tex}{\bf Fig.\,11{\it A}}).
In the dendrite the Ca$^{2+}$ -activated K$^+$ channels played acritical role in the dual function of the CaP channel in generatingCa$^{2+}$ spikes as well as dendritic plateaus. Becausethe K2 channel is sensitive to small changes in Ca$^{2+}$ concentrationit could effectively increase the threshold forCa$^{2+}$ spike generation by counteracting the activation ofsmall numbers of CaP channels. The involvement of theK2 channel in these two very different forms of dendriticresponse, and the presence of other mechanisms in the Purkinje
cell dendrite that through changes in the Ca$^{2+}$ concentration\,\cite{Llano:1991kx, Takei:1992ac}could activatethis channel, suggest interesting possibilities for regulationof more global dendritic response properties by the K2channel and other Ca$^{2+}$-inactivated K$^+$ channels that werenot included in the model (like the SK or afterhyperpolarization(AHP) current,\,\cite{Lancaster:1991ye}.
The model supports the suggestion that the channels responsiblefor generating plateau potentials are different inthe soma and dendrite\,cite{R:1980ly}. However,examination of the model also makes clear that thesedifferent plateaus are not physiologically isolated. A somaticplateau potential was always accompanied by a dendriticplateau and vice versa, because any depolarizationwill spread throughout the cell.
Other interactions between channels, like the activationof the anomalous rectifier during prolonged hyperpolarizations,followed by an activation of CaT channels during therebound spike, were not explored in detail. The anomalousrectifier did not affect the repetitive firing properties of themodel because it was completely deactivated beyond spiking threshold.

\bibliographystyle{plain}
\bibliography{../tex/bib/g3-refs.bib}

\end{document}
