\documentclass[12pt]{article}
\usepackage{verbatim}
\usepackage[dvips]{epsfig}
\usepackage{color}
\usepackage{url}
\usepackage[colorlinks=true]{hyperref}

\begin{document}

\section*{GENESIS: Documentation}

{\bf Related Documentation:}
% start: userdocs-tag-replace-items related-do-nothing
% end: userdocs-tag-replace-items related-do-nothing

\section*{Purkinje Cell Model--De Schutter}

\subsubsection*{Maximum conductances}

\begin{table}[!h]
\label{table:T2}
\caption{$\bar g$ for the voltage and Ca$^{2+}$-dependent channels in 2 different versions of the Purkinje cell model.}
\begin{tabular}{ l c c c c c c }  
                    &                     &                                          &                                       &                     &                            &                                                       \\
                    & \multicolumn{3}{ c} {\bf PM9 Model} &  \multicolumn{3}{ c} {\bf PM10 Model}                                                                                   \\
{\bf Name} & {\bf Soma} & {\bf Main Dendrite}       & {\bf Rest of Dendrite} & {\bf Soma} & {\bf Main Dendrite} & {\bf Rest of Dendrite}          \\
NaF            & 7,500          & 0.0                                   & 0.0                                & 7,500          & 0.0                     & 0.0                                                  \\
NaP            & 1.0              & 0.0                                    & 0.0                               & 1.0               & 0.0                     & 0.0                                                  \\
CaP            & 0.0              & 4.5                                    & 4.5                               & 0.0               & 4.0                     & 4.5                                                  \\
CaT            & 0.5              & 0.5                                    & 0.5                                & 0.5               & 0.5                     & 0.5                                                  \\
Kh               & 0.3              & 0.0                                    & 0.0                               & 0.3               & 0.0                     & 0.0                                                  \\
Kdr             & 600.0          & 60.0                                  & 0.0                               & 900.0           & 90.0                   & 0.0                                                  \\
KM              & 0.040         & 0.010                                & 0.013                          & 0.140           & 0.040                 & 0.013                                             \\
KA              &15.0             & 2.0                                     & 0.0                              & 15.0             & 2.0                      & 0.0                                                  \\
KC              & 0.0              & 80.0                                   & 80.0                            & 0.0               & 80.0                    & 80.0                                                \\
K2              & 0.0              & 0.39                                    & 0.39                            & 0.0               & 0.39                   & 0.39                                                \\
                   &                     &                                            &                                      &                     &                             &                                                         \\
\multicolumn{7}{l}{Extent of the main dendrite is shown in \href{../pub-purkinje-deschutter-fig-1/pub-purkinje-deschutter1-fig-1.tex}{\bf Figure\,1}.}                                                                                                                                 \\
\multicolumn{7}{l}{$\bar g$: maximum conductance mS/cm$^2$. For other abbreviations, see \href{../pub-purkinje-deschutter1-table1/pub-purkinje-deschutter1-table1.tex}{\bf Table\,1}.}                                               \\
\multicolumn{7}{l}{}                                                                                                                                                                                                                   \\
\end{tabular}
\end{table}

\subsection*{Channel Densities}

In the present model, simulations were started using initial
guesses for the $\bar g$ of the different channels in four zones of the cell,
i.e. the soma, the main dendrite, the smooth dendrites, and the
spiny dendrites (see Fig. 1). $\bar g$s were then altered until the model
could reproduce the characteristic firing behavior of Purkinje cells
during current injection in vitro\,\cite{R:1980ly, R:1980pi},
as described in Figs. 3--7. During this optimization
process it was not necessary to distinguish between
the smooth and spiny dendrites. In addition, optimal performance
required that the Kdr and A currents be present in the
main dendrite as well as in the soma.

Also, several combinations of $\bar g$ were found that could account for
the responses of Purkinje cells to current injection. For contrast,
versions PM9 and PM10 are presented, where PM10 represents
a Purkinje cell with higher K$^+$ channel densities, i.e., a leakier
cell.

\subsection*{Robustness to Changes in Channel Densities}

The principle parameters used to tune thismodel to the current injection data were the distributionand density of specific ion channels. Although Table\,\ref{table:T2} describedthe final distribution for this model, it was also importantto determine how sensitive the modeling resultswere to these particular density values.
A full search of the 10,000 dimensional parameter spacefor this model would have been computationally prohibitive(see\,\cite{S:1993dz}). Accordingly, the approachwe have taken involved examining the effect ofchanging the density of a single-channel type on the physiologicalresponses to current injection in the soma. The resultsshowed, perhaps not surprisingly, that small-amplitudecurrents like NaP and CaT currents, KA, or KM couldbe completely removed with little effect, except for smallchanges in firing frequency. The same was true for increasingKA or KM by a factor of 2 or 3. Similar increases inNaP or CaT currents, however, caused fast spiking in thesoma to saturate (as in \href{../pub-purkinje-deschutter1-fig-3/pub-purkinje-deschutter1-fig-3.tex}{\bf Fig.\,3D}) at lower current amplitudesand could turn the cell into a spontaneously firing orbursting neuron.
The model was more sensitive to changes of the conductancesinvolved in spike generation and repolarization.Small changes resulted in a shift of the $f-I$ curve and of thecurrent amplitude at which dendritic spiking started.Changes in the dendritic currents involved in spiking couldsuppress all dendritic spiking (reducing CaP current by220\,\%, increasing Kdr by $>$\,40\,\%, KC by 25\,\%, or K2 by10\,\% ) or make dendritic bursting the unique mode of firingof the cell (reducing NaF current by 50\,\%, increasing CaPcurrent by 50\,\%, or decreasing Kdr by 20\,\% or KC or K2 by10\,\%). NaF current could be reduced by 70\,\% before NaFspikes disappeared.
The model was thus sensitive to small changes in densityof CaP, KC, and K2 currents; in other words, the region ofparameter space that generated correct model responseswas not very large for these currents. Note, however, thatlarger changes could be applied to these channel densities ifone of the other current densities was changed in the oppositedirection. The model was less sensitive to changes in theother currents, like for example the densities of voltage-dependentK+ currents (cf. Table\,\cite{table:T2}).

\subsection*{Channel Distributions}

The density and distribution of channels in the model were the mainuncontrolled variables in these simulations. Experimentaltechniques do not yet exist to give detailed distribution anddensity information for all ionic channels in a given cell.Accordingly, by searching parameter space, detailed single cellmodels can make predictions concerning this criticalinformation\,\cite{S:1993dz}. In the current case,the initial channel distributions were primarily based on thespeculations of\,\cite{R:1980ly, R:1980pi}. The resultsof the model largely confirm these predictions with a fewmodifications.

\bibliographystyle{plain}
\bibliography{../tex/bib/g3-refs.bib}

\end{document}
