\documentclass[12pt]{article}
\usepackage{verbatim}
\usepackage[dvips]{epsfig}
\usepackage{color}
\usepackage{url}
\usepackage[colorlinks=true]{hyperref}

\begin{document}

\section*{GENESIS: Documentation}

\section*{SSP Regression Tests}

The Simple Scheduler in Perl ({\bf SSP}) integrates activation of the \href{../model-container/model-container/.tex}{\bf Model Container} and \href{../heccer/heccer.tex}{\bf Heccer} during a simulation.

For more details see the \href{../ssp/ssp.tex}{\bf SSP} documentation.

\subsection*{Obtaining Regression Test Specifications}

This \href{http://neurospaces.sourceforge.net/neurospaces_project/studio/tests/html/index.html}{\bf link} accesses all regression test specifications for {\bf SSP}.

\subsection*{Regression Test Documentation}

{\bf SSP} regression test documentation includes:
\begin{itemize}
\item The startup command.
\item The input to the test.
\item The expected output of the test.
\end{itemize}
The regression tests give a good overview of {\bf SSP} functionality. They consist of either {\bf SSP} stand-alone or integration tests with either {\bf Heccer} alone or with {\bf Heccer} and the {\bf Model Container}.

\subsection*{Scope of Regression Tests}

Regression tests cover the following major functionalities of {\bf SSP}:
\begin{itemize}

\item[]\href{http://neurospaces.sourceforge.net/neurospaces_project/ssp/tests/html/specifications/builtins/main.html}{\bf Built-ins}

Cell built-in schedule; cell built-in schedule applied to the Purkinje cell model.

\item[]\href{http://neurospaces.sourceforge.net/neurospaces_project/ssp/tests/html/specifications/integration/main.html}{Integration}

{\bf Heccer} aggregator options and related high-level gate tabulation interfacing; simple passive model; active model in passive testing mode; perfect clamp; pool integration; Purkinje model; spiking behavior; synaptic channels; raw gate tabulation calculations and high-level interfacing. 

\item[]\href{http://neurospaces.sourceforge.net/neurospaces_project/ssp/tests/html/specifications/integration/active/main.html}{Active Models}

Single and multiple active compartments; interaction between regular HH channels; 

\item[]\href{http://neurospaces.sourceforge.net/neurospaces_project/ssp/tests/html/specifications/integration/heccer/main.html}{\bf Heccer}

Simple passive model testing; pool integration.

\item[]\href{http://neurospaces.sourceforge.net/neurospaces_project/ssp/tests/html/specifications/integration/segments/main.html}{Segments}

Purkinje cell segments.

\item[]\href{http://neurospaces.sourceforge.net/neurospaces_project/ssp/tests/html/specifications/optimization/main.html}{Optimization}

Various duplicate tests repeated with the {\it -\,-\,optimize} flag.

\item[]\href{http://neurospaces.sourceforge.net/neurospaces_project/ssp/tests/html/specifications/ssp/main.html}{\bf SSP}

Command line switches; run-time versioning.

\end{itemize}

\end{document}
