\documentclass[12pt]{article}
\usepackage{verbatim}
\usepackage[dvips]{epsfig}
\usepackage{color}
\usepackage{url}
\usepackage[colorlinks=true]{hyperref}

\begin{document}

\section*{GENESIS: Documentation}

{\bf Related Documentation:}
% start: userdocs-tag-replace-items related-do-nothing
% end: userdocs-tag-replace-items related-do-nothing

\section*{De Schutter: Purkinje Cell Model}

\subsection*{RESPONSES TO CHANNEL BLOCKERS}

A second measure ofmodel robustness is its ability to replicate physiological datain response to standard channel blockers. In this case wecompared model results with\,\cite{R:1980ly} in response to both Na$^+$ and Ca$^{2+}$ channelblockers while holding all other model parameters fixed.
\href{../pub-purkinje-deschutter1-fig-9/pub-purkinje-deschutter1-fig-9.tex}{\bf Figure 9{\it A}} shows a simulation of TTX block (the conductanceof the NaF and NaP channels was set to 0) during a1.0\,nA current injection. Note that the somatic recordingshowed only attenuated dendritic spikes in the soma, therewere no fast somatic spikes, and that there was a sustainedplateau potential after the end of the current injection.Subthreshold current injection (0.1\,nA) only evoked theplateau current. Similar to the results of\,\cite{R:1980ly} (their Fig.\,6), Na$^+$ channel blockers selectivelyinterfered with somatic spikes while having little effect ondendritic spiking and plateau potentials. However, the dendriticspikes in the model were smaller and less sharp thanthose in experimental recordings. Also, contrary to experimentalresults, the plateau potential did not decay.
From these simulations one can conclude that dendriticspiking in the model was caused by the slow progressivedepolarization induced by the current injection, not by thelarger depolarizations during fast somatic spikes.
A simulation of Co$^{2+}$ block (the conductance of CaT and
CaP currents was set to 0) is shown in \href{../pub-purkinje-deschutter1-fig-9/pub-purkinje-deschutter1-fig-9.tex}{\bf Fig.\,9{\it B}}. Current
injection caused a slow depolarizing response that generatedfast somatic action potentials. With increasing amplitudeof currents there was less delay before the first actionpotential, but the spikes also decreased in amplitude andsaturated at a sustained plateau depolarization of about-30\,mV. These results are comparable with experimentalrecordings, except that higher-amplitude current injectionswere necessary in the model to obtain saturation of spiking.As in the case of\,\cite{R:1980ly} (their Fig.\,8), Ca$^{2+}$ channel blockers selectively interfered with dendriticspikes while leaving somatic plateau potentials andsomatic spiking intact. However, because the depolarizationcould not evoke dendritic Ca$^{2+}$ spikes, there was alsono Ca$^{2+}$-activated hyperpolarization to repolarize the cell
and the model settled in sustained plateaus with high-intensitycurrent injection. The model thus confirmed the importanceof dendritic Ca$^{2+}$-activated K$^+$ conductances inrepolarizing the somatic depolarizing spike bursts.

\bibliographystyle{plain}
\bibliography{../tex/bib/g3-refs.bib}

\end{document}
