\documentclass[12pt]{article}
\usepackage{verbatim}
\usepackage[dvips]{epsfig}
\usepackage{color}
\usepackage{url}
\usepackage[colorlinks=true]{hyperref}

\begin{document}

\section*{GENESIS: Documentation}

{\bf Related Documentation:}
% start: userdocs-tag-replace-items related-do-nothing
% end: userdocs-tag-replace-items related-do-nothing

\section*{GENESIS Components}

The GENESIS software platform is based on the
\href{../genesis-overview/genesis-overview.tex}{\bf
  CBI\,Federated\,Software\,Architecture}. This provides a modular
paradigm that places stand-alone software components into logical
relationships.  The management of these components is done with the
\href{../developer-package/developer-package.tex}{\bf
  GENESIS\,Developer\,Package}, a set of developer utilities that
integrate other components of GENESIS 3.  The following GENESIS
\href{../reserved-words/reserved-words.tex}{\bf Components} have been
implemented and tested and are currently compliant with the CBI
architecture (alphabetical order).

\begin{itemize}
   \item[]\href{../chemesis-3-log/chemesis-3-log.tex}{\bf Chemesis-3}: a simple reaction-diffusion solver.
   \item[]\href{../developer-package/developer-package.tex}{\bf Developer\,Package}: developer utilities that comply for GENESIS 3.
   \item[]\href{../documentation-overview/documentation-overview.tex}{\bf Documentation\,System}: all you need to know about installing, using and simulating using GENESIS 3.
   \item[]\href{../exchange/exchange.tex}{\bf Exchange}: Model exchange using common standars such as NeuroML and NineML.
   \item[]\href{../experiment/experiment.tex}{\bf Experiment}: Experimental protocols.
   \item[]\href{../gshell/gshell.tex}{\bf G-Shell}: Interactive GENESIS shell environment.
   \item[]\href{../gtube/gtube.tex}{\bf G-Tube}: GENESIS GUI.
   \item[]\href{../heccer/heccer.tex}{\bf Heccer}: Mathematical solver.
   \item[]\href{../model-container/model-container.tex}{\bf Model\,Container}: Solver-independent model storage.
   \item[]\href{../ns-sli/ns-sli.tex}{\bf NS-SLI}: GENESIS 2 \href{../backward-compatibility/backward-compatibility.tex}{\bf Backward\,Compatibility}.
   \item[]\href{../project-browser/project-browser.tex}{\bf Project\,Browser}: Inspect and compare simulation output.
   \item[]\href{../ssp/ssp.tex}{\bf SSP}: Simple Scheduler in Perl.
   \item[]\href{../studio/studio.tex}{\bf Studio}: Visualize models in the {\bf Model\,Container}.
\end{itemize}

\end{document}
